%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Author : Barbora Smondrkova, Tomas Polasek (template)
% Description : First exercise in the Introduction to Game Development course.
%   It deals with an analysis of a selected title from the point of its genre, 
%   style, and mechanics.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[a4paper,10pt,english]{article}

\usepackage[left=2.50cm,right=2.50cm,top=1.50cm,bottom=2.50cm]{geometry}
\usepackage[utf8]{inputenc}
\usepackage{hyperref}
\hypersetup{colorlinks=true, urlcolor=blue}

\newcommand{\ph}[1]{\textit{[#1]}}

\setlength{\parskip}{1em} 
%\setlength{\parindent}{0pt}

\title{%
Analysis of Mechanics%
}
\author{%
Barbora Šmondrková (xsmond00)%
}
\date{}

\begin{document}

\maketitle
\thispagestyle{empty}

{%
\large

\begin{itemize}

\item[] \textbf{Title:} Uncharted\,:\,Drake's Fortune

\item[] \textbf{Released:} 2007

\item[] \textbf{Author:} Amy Hennig, Naughty Dog

\item[] \textbf{Primary Genre:} Action-adventure

\item[] \textbf{Secondary Genre:} Third-person shooter

\item[] \textbf{Style:} Realistic

\end{itemize}

}

\section*{\centering Analysis}

% introduction
Uncharted is primarily an action-adventure game developed by Naughty Dog and created by Amy Hennig. Uncharted\,:\, Drake's Fortune came out in 2007 and later developed into a franchise with several sequels following the first game. In this analysis, I will focus on the first game in this franchise. However, the game genre and style persist in all of the sequels. 

% adventure
The game follows a treasure hunter, Nathan Drake, who seeks great treasures and mysteries. During his adventure, he is met with several challenges and puzzles that must be resolved to continue his adventure. The game introduces climbing passages, where he needs to find the correct way and climb through different terrain. Climbing is usually the easier challenge he needs to face. After climbing and exploring, he is met with puzzles that must be solved to continue. Nathan uses his sketch notebook to write all the information he collects on his adventure. This notebook provides clues and Nathan's train of thought. These passages provide the proper adventure experience, which gives the player a great amount of time to explore and think of a way to progress further. They provide a rest from the action passages, which usually follow right after.

% action
When Drake is met with the protagonist of his story the proper action starts. Other treasure hunters seek the same fortune, following a simple rule: first come, first served. Drake has to fight with the protagonist's armed forces that appear throughout the whole adventure. Drake has two machine guns, one pistol and one rifle, and four grenades which help him in his fight, nothing more. The difficulty of the battle changes each passage, and Nathan needs to find a proper strategy to kill all the forces. He can switch machine guns as he goes but always has to keep only one pistol and rifle. That is why he sometimes needs to decide which rifle is better in which situations.

% how does the action-adventure and third-person shooter blend
The game alternates between exploration, climbing, puzzle solving, and action-packed gunfights. It gives the game a sort of balance. where the player has the time to prepare and enjoy the exploration to be then taken into immersive gunfights, where the player thinks only about survival. Puzzle-solving adds a need for logical thinking, which can be, at times, frustrating, but it gives new meaning to the game where violence is not the only option how to progress further. 

% realistic style and cinematic experience from realistic style and strong story
The player plays as the mentioned Nathan Drake and makes the player feel as if they were Nathan Drake himself. This is also the reason why this analysis was written from Drake's point of view. The player is not just following his adventure, they are living this adventure. This game's story-telling and cinematic aspects make the player feel part of the environment and connected to Drake on different levels. The realistic style and the third-person view help to keep the atmosphere and help to keep the player immersed. Everything is blended to create a cinematic experience with a strong story and simple but active gameplay.

\end{document}
